Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2024-02-07 writing/paper_mcd19a2.qmd
Map the day with median improvement, not median MSE.

@fig-map-median-mse shows a tile on `r tar_read(median.mse.map.data)$date`.

```{r pred.map.median.mse}
#| label: fig-map-median-mse
#| fig-cap: !expr caption
caption = sprintf("Maps of typical MAIAC and Corrected AOD. Day selected as having the median improvement in MSE at AERONET sites. The map is centered on %s.",
    tar_read(median.mse.map)$center.name)
IG(tar_read(pred.map.median.mse.path))
```

>>>>

@fig-map-improve-mse shows a tile on `r tar_read(improve.mse.map.data)$date`.

```{r pred.map.median.improve}
#| label: fig-map-median-improve
#| fig-cap: !expr caption
caption = sprintf("Maps of typical MAIAC and Corrected AOD. Day selected as having the median improvement in MSE at AERONET sites. The map is centered on %s.",
    tar_read(median.improve.map)$center.name)
IG(tar_read(pred.map.median.improve.path))
```
